Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-03 paper/paper.Rmd
add explanation to section 5: case study

set.seed(42)

# equal to `tsk("ecuador")`
b = mlr3::as_data_backend(ecuador)
b$hash = "_mlr3_tasks_ecuador_" # optional
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "EPSG:32717")
)
```

>>>>

set.seed(42)
```

To set up the task `"ecuador"` manually, we would have to proceed as follows:

```{r create-task}
# equivalent to 'tsk("ecuador")':
b = mlr3::as_data_backend(ecuador)
b$hash = "_mlr3_tasks_ecuador_" # optional
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "EPSG:32717")
)
```
